Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

\def\vgap{\vspace{0mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-4mm}}

@@

\begin{figure*}
    \begin{tabular}{cccc}
        \includegraphics[height=30mm]{./artwork/prob-a} &
        \includegraphics[height=30mm]{./artwork/prob-b} &
        \includegraphics[height=30mm]{./artwork/prob-c} &
        \includegraphics[height=30mm]{./artwork/prob-a} \\
        (a) Problem $\EuScript{A}$ &
        (b) Problem $\EuScript{B}$ &
        (c) Problem $\EuScript{C}$ &
        (d) Problem $\EuScript{D}$
    \end{tabular}

@@

@@

>>>>

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-4mm}}

@@

\begin{figure*}
    \begin{tabular}{cccc}
        \includegraphics[height=30mm]{./artwork/prob-a} & 
        \hspace{3mm}
        \includegraphics[height=30mm]{./artwork/prob-b} &
        \hspace{3mm}
        \includegraphics[height=30mm]{./artwork/prob-c} &
        \hspace{3mm}
        \includegraphics[height=30mm]{./artwork/prob-d} \\
        (a) Problem $\EuScript{A}$ &
        \hspace{3mm}
        (b) Problem $\EuScript{B}$ &
        \hspace{3mm}
        (c) Problem $\EuScript{C}$ &
        \hspace{3mm}
        (d) Problem $\EuScript{D}$
    \end{tabular}

@@

\extraspacing {\bf Problem $\bm{\EuScript{D}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles, all in 2D space. The goal is to report, for each rectangle $r \in R$, all the segments $h \in H$ crossing $r$. Furthermore, those segments need to be sorted by their y-coordinates. Formally, if $h_1, h_2, ..., h_t$ (for some $t \ge 1$) are all the segments in $H$ crossing $r$, we output $(r: h_1, h_2, ..., h_t)$, provided that $y_i > y_{i-1}$ for each $i \in [2, t]$ where $y_i$ (resp., $y_{i-1}$) is the y-projection of $h_i$ (resp., $h_{i-1}$). Figure~\ref{fig:probs}d gives an example where $H = \set{h_1, h_2, h_3}$ and $R = \set{r_1, r_2}$; the output is $\set{(r_1: h_3, h_2), (r_2: h_2, h_1)}$.

In Appendix~\ref{app:prob-d}, we explain how to solve the problem in $O(n \log n + \out)$ time where $n = |H| + |R|$ and $\out$ is the number of pairs $(h, r) \in H \times R$ such that $h$ crosses $r$.

@@

\section{Algorithm for Problem $\bm{\EuScript{D}}$} \label{app:prob-d}
